Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-06-07 paper.tex
Making final changes.

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
star formation -- methods:numerical -- cosmology
\end{keywords}

@@

Once a halo becomes chemically enriched by the death of its Pop III stars, then by definition, it can no longer form more Pop III stars. This marks the end of metal-free star formation in that pregalactic object. Understanding the mixing of metals into the environment of these halos is necessary to constrain the reach of these metals and the effects they have for future star formation. Numerical studies have shown that turbulence within halos can mix metals well down to their resolution limit \citep{Wise08_Gal, Greif10, Smith15}. Stars will continue to form in halos, but with an increased metal abundance, these stars are now labeled as metal-enriched stars. These stars still are metal-poor, having metallicities of 10$^{-6}$ to 10$^{-2}$ of the solar abundance \citep{Chiaki16, Chiaki18, Ritter16}, have a direct chemical connection to Pop III stars, and survive until the present day \citep{Gnedin06, Tumlinson10, Griffen18, Magg18, Ezzeddine19}. Understanding the formation and chemical abundance of second generation stars can provide more evidence and insight for the earlier generation of Pop III stars.

Without metals and dust to facilitate efficient radiative cooling, Pop III stars rely on \hh{} formation to cool the gas. These molecules are however fragile to dissociation from Lyman-Werner (LW) radiation in the energy range 11.2--13.6~eV, through the Solomon process \citep{Field66, Stecher67}. This is a two-step process through which H$_{2}$ is excited to a higher state, H$_{2}^{\ast}$, via absorption of a LW photon:
\begin{equation} \label{Solomon1}
	H_{2} + \gamma \rightarrow  H_{2}^{\ast}
\end{equation}
This excited state then has a probability of dissociating into two hydrogen atoms:
\begin{equation} \label{Solomon2}
	H_{2}^{\ast} \rightarrow H + H
\end{equation}

@@

Previous work have mainly investigated and established the lower limit for a halo to host Pop III stars, or for a halo to collapse. However, subsequent simulations have shown that they do not necessarily form at this minimum due to the aforementioned physical processes playing a role. \citet{Mebane18} used a semi-analytic model of early star formation and found that the LW background coming from the rapidly increasing supply of Pop III stars becomes responsible for suppressing Pop III star formation. \citet{Griffen18} also find that the LW background can significantly suppress the amount of potential sites for Pop III star formation.

Numerical simulations have also been employed to investigate collapse thresholds and Pop III star formation. \citet[hereafter M01]{Machacek01} found similar results to those mentioned previously, in that the LW feedback can suppress the collapse of small mass halos. They fit a simple analytic expression for the mass threshold of halos given a particular LW flux:
\begin{equation} \label{mthresh}
	M_{\rm TH} ( M_{\odot} ) = 1.25 \times 10^{5} + 8.7  \times 10^{5} \left( \frac{4 \pi J_{\rm LW}}{10^{-21}} \right)^{0.47} .
\end{equation}
We will compare our results with this relation in future sections. \citet{Yoshida03} also finds that cooling is inefficient in halos with a LW background > 0.01 J$_{\rm 21}$, although with sufficient \hh{} shielding, halos are able to cool in the given LW background radiation. In fact, \citet{Wise07_UVB} found that central shocks drive \hh{} formation, allowing the halo to cool in a LW background intensity of 1 J$_{21}$. They find that \hh{} cooling is always a dominant process, even in large LW background fluxes. \citet{OShea08} also find that Pop III star formation can occur in relatively high LW backgrounds, implying that the LW background may not be a complete indicator of whether or not Pop III stars will form in a given halo.

@@

A time-dependent LW optically thin radiation background is applied in the simulation. This was fit in W12 (see their Eq. 16) and is consistent with the values in \citet{Trenti09_SFR}. The background evolution of the specific intensity takes the following form:
\begin{equation} \label{LWbg}
	\log_{10}(J_{\rm LW}/J_{21}) = A + Bz - Cz^{2} + Dz^{3} - Ez^{4}
\end{equation}
where $(A, B, C, D, E)$ = $(-2.567, 0.4562, - 0.02680, 5.882 \times 10^{-4}, - 5.056 \times 10^{-6})$ and J$_{21}$ is a specific intensity of 10$^{-21}$ erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$ sr$^{-1}$.  This form only varies by a factor of five in $z = 9-25$ and has a maximum of $J_{\rm LW}/J_{21} = 0.97$ at a redshift of 13.5 and slowly declines to 0.60 $J_{21}$ at $z = 9.3$ when we halt the simulation. We use adaptive ray tracing \citep{Abel02_RT, Wise11_Moray} to evolve the ionizing radiation field. Centered on each metal-enriched and Pop III star particle, we model the \hh{} dissociating radiation field with an optically thin, inverse square profile. These LW sources are added on top of the background intensity described above.
%====================================================================
\subsection{Star formation}
%====================================================================
In this section, we briefly discuss our implementation of Pop III and metal-enriched star formation. We do not consider the formation and feedback from stellar remnants or asymptotic giant branch (AGB) stars. For further details, we refer the reader to W12.

@@

If within 1 pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells. The mass of the Pop III star is randomly sampled from an initial mass function (IMF) of the form:
\begin{equation} \label{IMF}
	f(\log M)dM = M^{-1.3} \exp \left[-\left( \frac{M_{\rm char}}{M}\right)^{1.6} \right]dM
\end{equation}
where M$_{\rm char}$ = 20 M$_{\odot}$ \citep{Hirano17}. This characteristic mass is different from the W12 choice of 100 M$_{\odot}$. This results in an exponential cutoff before M$_{\rm char}$ and a power-law IMF after. Once the cell meets the above criteria and the stellar mass is chosen, an equal amount of gas is removed from the grid in a sphere which contains twice the stellar mass that is centered on the new star particle. The new Pop III star then gains the mass-weighted velocity of the gas contained within that sphere. In this simulation, we do not track any small scale fragmentation which may form low mass stars \citep{Greif11_P3Cluster}. We are only tracking massive Pop III star formation.

We use the mass-dependent hydrogen ionizing and LW luminosities and lifetimes from \citet{Schaerer02} and a mass-independent photon energy of E$_{\rm ph}$ = 29.6 eV, which is appropriate for the nearly mass-independent surface temperature of Pop III stars, at 10$^{5}$ K. A Type II supernova results if the Pop III star dies with a mass between 11 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 40. A pair instability supernova (PISNe) results if the star dies with a mass between 140 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 260. Outside of these mass ranges, the Pop III star dies as a black hole. In this simulation, no black hole physics are implemented, so the Pop III star simply turns into a collisionless particle. When 11 $\leq$ M$_{\star}$/M$_{\odot}$ < 20, the star dies as a normal Type II supernova with an energy of 10$^{51}$ erg. From 20 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 40, the star dies as a hypernova with energies taken from \citet{Nomoto06}. The PISNe have explosion energies from \citet{2002ApJ...567..532H}, of which the analytic function fit to their models can be seen in Eq. 12 of W12.

@@

%====================================================================
\subsection{Analytic Calculation of the Shielding Factor for a Static Halo}
%====================================================================
To demonstrate how the shielding factor changes as a function of halo mass and redshift, we can examine $N_{\rm H2}$ between the core and halo virial radius as a function of halo mass for an isothermal halo, with a constant \hh{} fraction, and use Equation \ref{shield} to calculate the shielding factor. The \hh{} molecule number density within the halo is given by 
\begin{equation} \label{numberh2}
	n_{\rm H2}(r) = f_{\rm H2} \frac{\rho_{0}R^{2}_{\rm vir}}{\mu m_{\rm H} r^{2}}
\end{equation}
where $\mu = 1.22$ is the mean molecular weight, $\rho_{0} = 200 \rho_{c} / 3$ is the density at the virial radius, and $\rho_{c} = 3 H_{0}^{2} / 8 \pi G (1+z)^3$ is the critical density. The column density is then equation \ref{numberh2} integrated from the radius of the core to the virial radius, where the core has a radius of $f_{c} R_{\rm vir}$: 
\begin{equation} \label{columnh2}
	N_{\rm H2} = f_{\rm H2} R_{\rm vir} \frac{200 \rho_{c}}{3 \mu m_{\rm H}} \left(\frac{1}{f_{c}} - 1 \right)
\end{equation}

For $\rm{H}_{0} = 70 \ \rm{km} \ \rm{s}^{-1} \ \rm{Mpc}^{-1}$, a typical \hh{} fraction of $f_{\rm H2} = 10^{-4}$, and assuming the Doppler broadening parameter, $b$, is equal to the circular velocity of the halo, Equation \ref{columnh2} and Equation \ref{shield} will give the shielding factor for a given core radius, $f_{c}$, and redshift. Figure \ref{fig:shield_mass} shows the shielding factor as a function of halo mass, for redshifts $z = 9$, $15$, and $25$ in red, blue and black, respectively. The solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines a core radius of $f_{c} = 10^{-4}$. Across the top axis and plotted as a green line, the shielding factor as a function of \hh{} column density is shown for a circular velocity of 10 km/s. At each redshift, all halo masses, and for each core radius, we see the shielding factor is significantly smaller than one, implying that \hh{} shielding for these halos is almost at a maximum. The shielding factor will then significantly decrease the dissociation rate of \hh{}, allowing for the presence of \hh{} within a LW background. Smaller mass halos can then form Pop III stars since \hh{} will survive in the halo for a longer amount of time. We also see that for column densities at just under $10^{17} \rm cm^{-2}$, the shielding factor quickly drops to 0.1 for a halo with this particular circular velocity, showing that \hh{} shielding can affect the dissociation rate of \hh{} at relatively low column densities.

\begin{figure}
	\includegraphics[width=\columnwidth]{images/shield_mass.pdf}
    \caption{Shielding factor as a function of halo mass. Solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines indicate a core radius of $f_{c} = 10^{-4}$. For these parameters, and assuming the Doppler broadening parameter equals the circular velocity, the shielding factor is almost zero, implying maximum shielding. The green line shows the shielding factor as a function of \hh{} column density for a circular velocity of 10 km/s. }
    \label{fig:shield_mass}
\end{figure}
%====================================================================
\section{Results}
%====================================================================
In this section, we will present the distribution of host halo masses of Pop III stars, the relation between the mass distribution and the LW background radiation, and the distribution of various Pop III properties.

To ensure that our box is representative of a typical piece of the universe, Figure \ref{fig:hmf} shows the simulated halo mass function along with the analytic Sheth-Tormen mass function at $z = 9.3$. The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve below 10$^{5}$ M$_{\odot}$ halos that contain $\approx$ 50 particles. After a sufficient amount of time after the beginning of the simulation, enough matter has collapsed to begin forming Pop III stars throughout the box. These stars either become black holes or supernova at the end of their lives, with the latter resulting in an expulsion of metals into the star's surroundings. Metal-enriched star formation begins to take place as soon as enough metals are present within a halo. In the meantime, halos form and merge with one another, resulting in a wide variety of galaxies, and reionization starts to take place. By the end of the simulation, 20\% of the box has an ionized fraction over 10\%, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity as a function of time, and temperature projections of the box at certain points in time.

@@

In our simulation, 688 Pop III stars form between 27.23 $\geq z \geq$ 9.39. The corresponding star formation rate density (SFRD) can be seen in Figure \ref{fig:pop3_SFR_bar}, peaking at $1.9 \times 10^{-4}$ at $z = 21.3$ and slowly decreases. The SFRD sharply declines near the end of the simulation but does not drop to zero. Small volumes are subject to cosmic variance, in particular the formation time of the first galaxies, which generates the bulk of the LW radiation background.  This SFRD is therefore not representative of a cosmological average.  In particular, it decreases at $z \le 11$ when the most massive galaxy undergoes an extended period of star formation, boosting the local LW radiation field as shown in Figure \ref{fig:JLW_xe_mass}.  The rates are consistent with other studies \citep[e.g.][]{Xu13, Magg16}, but it is likely to change depending on the particular modes captured by the initial conditions.

\begin{figure}
	\includegraphics[width=\columnwidth]{images/pop3_SFR_bar.pdf}
    \caption{The star formation rate density of Pop III stars. The SFRD peaks at a redshift of 20, and slowly falls off. Note that metal-enriched star formation continually increases throughout time, although that is not plotted here. Due to the small box size of our simulation, this SFRD is particular for our box, and would change for larger, or smaller box sizes.}
    \label{fig:pop3_SFR_bar}
\end{figure}

%====================================================================
\subsection{Population III host halo masses}
%====================================================================
 To determine the host halos of new Pop III stars, we use the halo finding code, \rockstar{} \citep{rockstar}. The mass determined by \rockstar{} is the dark matter mass, so to determine the total mass of the halos, we multiply the masses by $\Omega_{\rm M}/\Omega_{\rm DM}$. The total mass is subsequently used in our analysis. We also take the center and virial radius from the \rockstar{} halo catalog. A small percentage of Pop III stars do not form in a halo identified by \rockstar{}. Assuming that Pop III stars must form in collapsed halos, we calculate the virial mass and radius of a halo centered on the Pop III star directly from the simulation data. We calculate the LW intensity impinging on each halo by summing up the contribution coming from each radiating star particle outside the virial radius of the host halo. This is then added to the constant LW background implemented in the simulation (Eq. \ref{LWbg}). In this work, we only analyze halos below the atomic cooling limit.

In redshift bins of $\Delta z$ = 1, the mean halo mass hosting Pop III stars is determined, and plotted as black dots against the redshift bins in Figure \ref{fig:mean_mass}. The median for each bin is represented by an x, and the 15.9 and 84.1 percentiles are plotted below and above the mean, respectively. The M01 relation (Equation \ref{mthresh}) for our LW background intensity in Eq. \ref{LWbg} is shown as the black solid line. Notably, the mean halo mass falls well below the relation, at $<10^{6}$ M$_{\odot}$ until $z = 15$ (270 Myr), at which point, the mean halo mass steadily rises above $3 \times 10^{6}$ M$_{\odot}$. The large discrepancy between our data and the mass threshold from M01 is indicative of the \hh{} shielding which is included in our simulation. \hh{} shielding allows for halos to cool at much lower masses, and therefore, Pop III stars are forming in these halos at earlier times. In the M01 analysis, \hh{} shielding is neglected in their calculations for a variety of reasons, including the Doppler broadening of LW bands and large column densities of \hh{} only beginning to form at late times. Interestingly, a full radiation hydrodynamics simulation, such as ours, does not produce identical results as M01 predicts. Throughout the literature, there appears to be a consensus that \hh{} self-shielding will help smaller mass halos collapse in the presence of a LW background radiation \citep[E.g.][]{Yoshida03, Ricotti01, Glover01, Hartwig15}. As can be seen by the red solid line in \ref{fig:mean_mass}, nearly 100\% of the halos hosting Pop III stars fall below the M01 relation, until around a redshift of 15, at which point, the mean halo mass begins to rise above the relation. The increase in the mean halo mass above the M01 relation is indicative of the increased LW intensity permeating the box due to a galaxy that becomes very active in star formation at late times. This galaxy has a halo mass of $3.6 \times 10^{8} \rm M_{\odot}$, a total stellar mass of $3.1 \times 10^{6} \rm M_{\odot}$, and has a peak Pop III SFR of $2.7 \times 10^{-4}\, \rm M_{\odot} yr^{-1}$ at $z=15$ (250 Myr) and a peak metal enriched SFR of $5.4 \times 10^{-2}\, \rm M_{\odot} yr^{-1}$ at $z=9.5$ (500~Myr). This galaxy produces a large amount of LW radiation which dominates the box, and drives up the minimum halo mass required for the formation of Pop III stars. This increase in the LW background can also be seen in Figure \ref{fig:JLW_xe_mass}, where by the end of the simulation, the LW background rises to greater than 1 $J_{21}$.

@@

The LW background intensity versus the host halo mass for each Pop III halo in our dataset is shown in Figure \ref{fig:jlw_mass_machacek}. Because the LW background only varies by a factor of five as Pop III stars form, most points lie within a small intensity range, just below $1~J_{21}$. Each point is colored by the redshift where the Pop III star forms and the mass threshold from M01 (Eq. \ref{mthresh}) for the given LW background (Eq. \ref{LWbg}) is the solid black line. We see again that almost all halos form Pop III stars below the M01 threshold. There are also a few halos that form Pop III stars in very high J$_{\rm LW}$, below the relation. This situation arises when there are multiple Pop III stars forming at about the same time, within $\approx$ 100 pc of each other. Star formation can occur in a neighboring halo of a Pop III star whose LW radiation does not have ample time to photodissociate enough \hh{} to completely suppress star formation. The high J$_{\rm LW}$ is generally an indicator that the halos will likely have their star formation suppressed, but in cases where Pop III star formation occurs synchronically, star formation will not be suppressed, so long as they are a suitable distance away from each other. As there are only a few data points in this region, this situation is rare. It should be noted that there are duplicate halos within this plot, since halos are allowed to form multiple Pop III stars if the conditions are sufficient and each point represents an instance of Pop III formation. The grouped points in the higher end of J$_{\rm LW}$ are representative of such halos.

@@

Finally with most studies of metal-free stars, there is the caveat of its uncertain IMF that affects the individual stellar luminosities and surface temperatures of the Pop III stars.  Changes in the IMF could alter the multiplicity and total stellar mass of the system because the radiative feedback from the earlier stars could affect the thermodynamics of other molecular clouds within the same halo.  Ultimately the IMF determines the fraction of stars going supernova and the metal production in pre-galactic objects that is the root cause of suppressing and ending Pop III star formation in the early universe.

>>>>

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
star formation  -- cosmology: first stars -- stars: Population III -- methods: numerical
\end{keywords}

@@

Once a halo becomes chemically enriched by the death of Pop III stars, then by definition, it can no longer form more Pop III stars. This marks the end of metal-free star formation in that pregalactic object. Understanding the mixing of metals into the environment of these halos is necessary to constrain the reach of these metals and the effects they have for future star formation. Numerical studies have shown that turbulence within halos can mix metals well down to their resolution limit \citep{Wise08_Gal, Greif10, Smith15}. Stars will continue to form in halos, but with an increased metal abundance. These stars still are metal-poor, having metallicities of 10$^{-6}$ to 10$^{-2}$ of the solar abundance \citep{Chiaki16, Chiaki18, Ritter16}, have a direct chemical connection to Pop III stars, and can survive until the present day \citep{Gnedin06, Tumlinson10, Griffen18, Magg18, Ezzeddine19}. Understanding the formation and chemical abundance of second generation stars can provide more evidence and insight for the earlier generation of Pop III stars.

Without metals and dust to facilitate efficient radiative cooling, Pop III stars rely on \hh{} formation in the gas-phase for cooling. These molecules are however fragile to dissociation from Lyman-Werner (LW) radiation in the energy range 11.2--13.6~eV, through the Solomon process \citep{Field66, Stecher67}. This is a two-step process through which H$_{2}$ is excited to a higher state, H$_{2}^{\ast}$, via absorption of a LW photon:
\begin{equation} \label{Solomon1}
	H_{2} + \gamma \rightarrow  H_{2}^{\ast}
\end{equation}
This excited state then has a probability of dissociating into two hydrogen atoms:
\begin{equation} \label{Solomon2}
	H_{2}^{\ast} \rightarrow H + H
\end{equation}

@@

Previous work have mainly investigated and established the lower limit for a halo to host Pop III stars, or for a halo to collapse. However, subsequent simulations have shown that they do not necessarily form at this minimum due to the aforementioned physical processes playing a role. \citet{Mebane18} used a semi-analytic model of early star formation and found that the LW background coming from the rapidly increasing supply of Pop III stars becomes responsible for suppressing Pop III star formation. \citet{Griffen18} also found that the LW background can significantly suppress the amount of potential sites for Pop III star formation.

Numerical simulations have also been employed to investigate collapse thresholds and Pop III star formation. \citet[hereafter M01]{Machacek01} found similar results to those mentioned previously, in that the LW feedback can suppress the collapse of small mass halos. They fit a simple analytic expression for the mass threshold of halos given a particular LW intensity J$_{\rm LW}$:
\begin{equation} \label{mthresh}
	M_{\rm TH} ( M_{\odot} ) = 1.25 \times 10^{5} + 8.7  \times 10^{5} \left( \frac{4 \pi J_{\rm LW}}{10^{-21}} \right)^{0.47} .
\end{equation}
We will compare our results with this relation in future sections. \citet{Yoshida03} also found that cooling is inefficient in halos with a LW background > 0.01 J$_{\rm 21}$, where J$_{\rm 21}$ is a specific intensity of 10$^{-21}$ erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$ sr$^{-1}$, although with sufficient \hh{} shielding, halos are able to cool in the given LW background radiation. In fact, \citet{Wise07_UVB} found that central shocks drive \hh{} formation, allowing the halo to cool in a LW background intensity of 1 J$_{21}$. They find that \hh{} cooling is always a dominant process, even in large LW background fluxes. \citet{OShea08} also found that Pop III star formation can occur in relatively high LW backgrounds, implying that the LW background may not be a complete indicator of whether or not Pop III stars will form in a given halo.

@@

A time-dependent LW optically thin radiation background is applied in the simulation. This was fit in W12 (see their Eq. 16) and is consistent with the values in \citet{Trenti09_SFR}. The background evolution of the specific intensity takes the following form:
\begin{equation} \label{LWbg}
	\log_{10}(J_{\rm LW}/J_{21}) = A + Bz - Cz^{2} + Dz^{3} - Ez^{4}
\end{equation}
where $(A, B, C, D, E)$ = $(-2.567, 0.4562, - 0.02680, 5.882 \times 10^{-4}, - 5.056 \times 10^{-6})$.  This form only varies by a factor of five in $z = 9-25$ and has a maximum of $J_{\rm LW}/J_{21} = 0.97$ at a redshift of 13.5 and slowly declines to 0.60 $J_{21}$ at $z = 9.3$ when we halt the simulation. We use adaptive ray tracing \citep{Abel02_RT, Wise11_Moray} to evolve the ionizing radiation field. Centered on each metal-enriched and Pop III star particle, we model the \hh{} dissociating radiation field with an optically thin, inverse square profile. These LW sources are added on top of the background intensity described above.
%====================================================================
\subsection{Star formation}
%====================================================================
In this section, we briefly discuss our implementation of Pop III and metal-enriched star formation. We do not consider the formation and feedback from stellar remnants or asymptotic giant branch (AGB) stars. For further details, we refer the reader to W12.

@@

If within 1 pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells. The mass of the Pop III star is randomly sampled from an initial mass function (IMF) of the form:
\begin{equation} \label{IMF}
	f(\log M)dM = M^{-1.3} \exp \left[-\left( \frac{M_{\rm char}}{M}\right)^{1.6} \right]dM
\end{equation}
where M$_{\rm char}$ = 20 M$_{\odot}$ \citep{Hirano17}. This characteristic mass is different from the W12 choice of 100 M$_{\odot}$. This results in an exponential cutoff below M$_{\rm char}$ and a power-law IMF above. Once the cell meets the above criteria and the stellar mass is chosen, an equal amount of gas is removed from the grid in a sphere which contains twice the stellar mass that is centered on the new star particle. The new Pop III star then gains the mass-weighted velocity of the gas contained within that sphere. In this simulation, we do not track any small scale fragmentation which may form low mass stars \citep{Greif11_P3Cluster}. We are only tracking massive Pop III star formation.

We use the mass-dependent hydrogen ionizing and LW luminosities and lifetimes from \citet{Schaerer02} and a mass-independent photon energy of E$_{\rm ph}$ = 29.6 eV, which is appropriate for the nearly mass-independent surface temperature of Pop III stars, at 10$^{5}$ K. A Type II supernova results if the Pop III star dies with a mass between 11 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 40. A pair instability supernova (PISNe) results if the star dies with a mass between 140 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 260. Outside of these mass ranges, the Pop III star dies as a black hole. In this simulation, no black hole physics are implemented, so the Pop III star simply turns into an inert collisionless particle. When 11 $\leq$ M$_{\star}$/M$_{\odot}$ < 20, the star dies as a normal Type II supernova with an energy of 10$^{51}$ erg. From 20 $\leq$ M$_{\star}$/M$_{\odot}$ $\leq$ 40, the star dies as a hypernova with energies taken from \citet{Nomoto06}. The PISNe have explosion energies from \citet{2002ApJ...567..532H}, of which the analytic function fit to their models can be seen in Eq. 12 of W12.

@@

%====================================================================
\subsection{Analytic Calculation of the Shielding Factor for a Static Halo}
%====================================================================
To demonstrate how the shielding factor changes as a function of halo mass and redshift, we can examine $N_{\rm H2}$ between the core and halo virial radius as a function of halo mass for an isothermal halo, with a constant \hh{} fraction, and use Equation \ref{shield} to calculate the shielding factor. The \hh{} molecule number density within the halo is given by 
\begin{equation} \label{numberh2}
	n_{\rm H2}(r) = f_{\rm H2} \frac{\rho_{0}R^{2}_{\rm vir}}{\mu m_{\rm H} r^{2}}
\end{equation}
where $\mu = 1.22$ is the mean molecular weight, $\rho_{0} = 200 \rho_{c} / 3$ is the density at the virial radius, and $\rho_{c} = 3 H_{0}^{2} / 8 \pi G (1+z)^3$ is the critical density. Here, H$_{0}$ is the Hubble constant, G is the gravitational constant, and z is the redshift. The column density is then equation \ref{numberh2} integrated from the radius of the core to the virial radius, where the core has a radius of $f_{c} R_{\rm vir}$: 
\begin{equation} \label{columnh2}
	N_{\rm H2} = f_{\rm H2} R_{\rm vir} \frac{200 \rho_{c}}{3 \mu m_{\rm H}} \left(\frac{1}{f_{c}} - 1 \right)
\end{equation}

For $\rm{H}_{0} = 70 \ \rm{km} \ \rm{s}^{-1} \ \rm{Mpc}^{-1}$, a typical \hh{} fraction of $f_{\rm H2} = 10^{-4}$, and assuming the Doppler broadening parameter, $b$, is equal to the circular velocity of the halo, Equation \ref{columnh2} and Equation \ref{shield} will give the shielding factor for a given core radius, $f_{c}$, and redshift. Figure \ref{fig:shield_mass} shows the shielding factor as a function of halo mass, for redshifts $z = 9$, $15$, and $25$ in red, blue and black, respectively. The solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines a core radius of $f_{c} = 10^{-4}$. Across the top axis and plotted as a green line, the shielding factor as a function of \hh{} column density is shown for a circular velocity of 10 km/s. At each redshift, all halo masses, and for each core radius, we see the shielding factor is significantly smaller than one, implying that \hh{} shielding for these halos is almost at a maximum. The shielding factor will then significantly decrease the dissociation rate of \hh{}, allowing for the presence of \hh{} within a LW background. Smaller mass halos can then form Pop III stars since \hh{} will survive in the halo for a longer amount of time. We also see that for column densities at just under $10^{17} \rm cm^{-2}$, the shielding factor quickly drops to 0.1 for a halo with this particular circular velocity, showing that \hh{} shielding can affect the dissociation rate of \hh{} in relatively low halo masses.

\begin{figure}
	\includegraphics[width=\columnwidth]{images/shield_mass.pdf}
    \caption{Shielding factor as a function of halo mass. Solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines indicate a core radius of $f_{c} = 10^{-4}$. For these parameters, and assuming the Doppler broadening parameter equals the circular velocity, the shielding factor is below 1 percent. The green line shows the shielding factor as a function of \hh{} column density for a circular velocity of 10 km/s. }
    \label{fig:shield_mass}
\end{figure}
%====================================================================
\section{Results}
%====================================================================
In this section, we will present the distribution of host halo masses of Pop III stars, the relation between the mass distribution and the LW background radiation, and the distribution of various Pop III properties.

To ensure that our box is representative of a typical piece of the universe, Figure \ref{fig:hmf} shows the simulated halo mass function along with the analytic Sheth-Tormen mass function at $z = 9.3$. The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve below 10$^{5}$ M$_{\odot}$ halos that contain $\approx$ 50 particles. After a sufficient amount of time after the beginning of the simulation, enough matter has collapsed to begin forming Pop III stars throughout the box. These stars either become black holes or supernovae at the end of their lives, with the latter resulting in an expulsion of metals into the star's surroundings. Metal-enriched star formation begins to take place as soon as enough metals are present within a halo. In the meantime, halos form and merge with one another, resulting in a wide variety of galaxies, and reionization starts to take place. By the end of the simulation, 20\% of the box has an ionized fraction greater than 10\%, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity as a function of time, and temperature projections of the box at certain points in time.

@@

In our simulation, 688 Pop III stars form between 27.23 $\geq z \geq$ 9.39. The corresponding star formation rate density (SFRD) can be seen in Figure \ref{fig:pop3_SFR_bar}, peaking at $1.9 \times 10^{-4} \ \rm M_{\odot} \ yr^{-1} \ Mpc^{-3}$ at $z = 21.3$ and slowly decreases. The SFRD sharply declines near the end of the simulation but does not drop to zero. Small volumes are subject to cosmic variance, in particular the formation time of the first galaxies, which generates the bulk of the LW radiation background.  This SFRD is therefore not representative of a cosmological average.  In particular, it decreases at $z \le 11$ when the most massive galaxy undergoes an extended period of star formation, boosting the local LW radiation field as shown in Figure \ref{fig:JLW_xe_mass}.  The rates are consistent with other studies \citep[e.g.][]{Xu13, Magg16}, but it is likely to change depending on the particular modes captured by the initial conditions.

\begin{figure}
	\includegraphics[width=\columnwidth]{images/pop3_SFR_bar.pdf}
    \caption{The star formation rate density of Pop III stars. The SFRD peaks at a redshift of 20, and slowly falls off. Note that metal-enriched star formation continually increases throughout time, although that is not plotted here. Due to the small box size of our simulation, this SFRD is particular for our box.}
    \label{fig:pop3_SFR_bar}
\end{figure}

%====================================================================
\subsection{Population III host halo masses}
%====================================================================
 To determine the host halos of new Pop III stars, we use the halo finding code, \rockstar{} \citep{rockstar}. The mass determined by \rockstar{} is the dark matter mass, so to determine the total mass of the halos, we multiply the masses by $\Omega_{\rm M}/\Omega_{\rm DM}$. The total mass is subsequently used in our analysis. We also take the center and virial radius from the \rockstar{} halo catalog. A small percentage of Pop III stars do not form in a halo identified by \rockstar{}. Assuming that Pop III stars must form in collapsed halos, we calculate the virial mass and radius of a halo centered on the Pop III star directly from the simulation data by determining the sphere that contains an average overdensity of 200 $\rho_{\rm c}$. We calculate the LW intensity impinging on each halo by summing up the contribution coming from each radiating star particle outside the virial radius of the host halo. This is then added to the constant LW background implemented in the simulation (Eq. \ref{LWbg}). In this work, we only analyze halos below the atomic cooling limit.

In redshift bins of $\Delta z$ = 1, the mean halo mass hosting Pop III stars is determined, and plotted as black dots against the redshift bins in Figure \ref{fig:mean_mass}. The median for each bin is represented by a cross, and the 15.9 and 84.1 percentiles are plotted below and above the mean, respectively. The M01 relation (Equation \ref{mthresh}) for our LW background intensity in Eq. \ref{LWbg} is shown as the black solid line. Notably, the mean halo mass falls well below the relation, at $<10^{6}$ M$_{\odot}$ until $z = 15$ (270 Myr), at which point, the mean halo mass steadily rises above $3 \times 10^{6}$ M$_{\odot}$. The large discrepancy between our data and the mass threshold from M01 is indicative of the \hh{} shielding which is included in our simulation. \hh{} shielding allows for halos to cool at much lower masses, and therefore, Pop III stars are forming in these halos at earlier times. In the M01 analysis, \hh{} shielding is neglected in their calculations for a variety of reasons, including the Doppler broadening of LW bands and large column densities of \hh{} only beginning to form at late times. Interestingly, a full radiation hydrodynamics simulation, such as ours, does not produce identical results as M01 predicts. Throughout the literature, there appears to be a consensus that \hh{} self-shielding will help smaller mass halos collapse in the presence of a LW background radiation \citep[e.g.][]{Yoshida03, Ricotti01, Glover01, Hartwig15}. As can be seen by the red solid line in Figure \ref{fig:mean_mass}, nearly 100\% of the halos hosting Pop III stars fall below the M01 relation, until around a redshift of 15, at which point, the mean halo mass begins to rise above the relation. The increase in the mean halo mass above the M01 relation is indicative of the increased LW intensity permeating the box due to a galaxy that becomes very active in star formation at late times. This galaxy has a halo mass of $3.6 \times 10^{8} \rm M_{\odot}$, a total stellar mass of $3.1 \times 10^{6} \rm M_{\odot}$, and has a peak Pop III SFR of $2.7 \times 10^{-4}\, \rm M_{\odot}\ yr^{-1}$ at $z=15$ (250 Myr) and a peak metal enriched SFR of $5.4 \times 10^{-2}\, \rm M_{\odot} \ yr^{-1}$ at $z=9.5$ (500~Myr). This galaxy produces a large amount of LW radiation which dominates the box, and drives up the minimum halo mass required for the formation of Pop III stars. This increase in the LW background can also be seen in Figure \ref{fig:JLW_xe_mass}, where by the end of the simulation, the LW background rises to greater than 1 $J_{21}$.

@@

The LW background intensity versus the host halo mass for each Pop III halo in our dataset is shown in Figure \ref{fig:jlw_mass_machacek}. Because the LW background only varies by a factor of five as Pop III stars form, most points lie within a small intensity range, just below $1~J_{21}$. Each point is colored by the redshift where the Pop III star forms and the mass threshold from M01 (Eq. \ref{mthresh}) for the given LW background (Eq. \ref{LWbg}) is the solid black line. We see again that almost all halos form Pop III stars below the M01 threshold. There are also a few halos that form Pop III stars in very high J$_{\rm LW}$, below the relation. This situation arises when there are multiple Pop III stars forming at about the same time, within $\approx$ 100 pc of each other. Star formation can occur in a neighboring halo of a Pop III star whose LW radiation does not have ample time to photodissociate enough \hh{} to completely suppress star formation. The high J$_{\rm LW}$ is generally an indicator that the halos will likely have their star formation suppressed, but in cases where Pop III star formation occurs at about the same time, star formation will not be suppressed, so long as they are a suitable distance away from each other. As there are only a few data points in this region, this situation is rare. It should be noted that there are duplicate halos within this plot, since halos are allowed to form multiple Pop III stars if the conditions are sufficient and each point represents an instance of Pop III formation. The grouped points in the higher end of J$_{\rm LW}$ are representative of such halos.

@@

Finally with most studies of metal-free stars, there is the caveat of its uncertain IMF that affects the individual stellar luminosities and surface temperatures of the Pop III stars.  Changes in the IMF could alter the multiplicity and total stellar mass of the system because the radiative feedback from the earlier stars can affect the thermodynamics of other molecular clouds within the same halo.  Ultimately the IMF determines the fraction of stars going supernova and the metal production in pre-galactic objects that is the root cause of suppressing and ending Pop III star formation in the early universe.
